NPH-MS-2020-34477.R1 - Response to review

### 2020-11-07 README.Rmd
tree link 📖

* `data` Primary germination data and species traits.
* `doc` Files to create the manuscript using `Rmarkdown`.
* `results` Output of the `R` scripts, including MCMCglmm analysis outputs.
* `src` Scripts in `R` language used to process data and perform the analyses of the manuscript.

>>>>

* `data` Primary data, including the [germination](https://github.com/efernandezpascual/alpineseeds/blob/master/data/germination.csv) dataset, the species [traits](https://github.com/efernandezpascual/alpineseeds/blob/master/data/traits.csv) and the phylogenetic [tree](https://github.com/efernandezpascual/alpineseeds/blob/master/data/ALPINE.tree.pdf).
* `doc` Files to create the manuscript using `Rmarkdown`.
* `results` Output of the `R` scripts, including [MCMCglmm analysis](https://github.com/efernandezpascual/alpineseeds/tree/master/results/MCMCglmm) outputs.
* `src` Scripts in `R` language used to process data and perform the analyses of the manuscript.

### 2020-11-07 doc/cover-letter.Rmd
tree link 📖

We have added to the text the number of species with values calculated from species-values, genus-averages or family-averages. We also added this information to the primary data available at the [GitHub repository](https://github.com/efernandezpascual/alpineseeds). We have indicated, in the relevant places of the text, which datasets ([germination](https://github.com/efernandezpascual/alpineseeds/blob/master/data/germination.csv), [species traits](https://github.com/efernandezpascual/alpineseeds/blob/master/data/traits.csv), and [phylogenetic tree](https://github.com/efernandezpascual/alpineseeds/blob/master/data/alpine.tree.pdf)) and results (detailed results of the [MCMCglmm analysis](https://github.com/efernandezpascual/alpineseeds/tree/master/results/MCMCglmm)) are available at GitHub.

@@

The phylogeny is available at the [GitHub repository](https://github.com/efernandezpascual/alpineseeds) as a [.tree file](https://github.com/efernandezpascual/alpineseeds/blob/master/data/ALPINE.tree) that can be imported into R, or opened with software like [TreeGraph](http://treegraph.bioinfweb.info/). We have now also included a [pdf version of the tree](https://github.com/efernandezpascual/alpineseeds/blob/master/data/alpine.tree.pdf), so it can be visualized directly. We have indicated at the appropriate point of the text that the tree can be accessed at GitHub. We would prefer this solution to including it as a supplementary file, to avoid duplicating data sources.

>>>>

We have added to the text the number of species with values calculated from species-values, genus-averages or family-averages. We also added this information to the primary data available at the [GitHub repository](https://github.com/efernandezpascual/alpineseeds). We have indicated, in the relevant places of the text, which datasets ([germination](https://github.com/efernandezpascual/alpineseeds/blob/master/data/germination.csv), [species traits](https://github.com/efernandezpascual/alpineseeds/blob/master/data/traits.csv), and [phylogenetic tree](https://github.com/efernandezpascual/alpineseeds/blob/master/data/ALPINE.tree.pdf)) and results (detailed results of the [MCMCglmm analysis](https://github.com/efernandezpascual/alpineseeds/tree/master/results/MCMCglmm)) are available at GitHub.

@@

The phylogeny is available at the [GitHub repository](https://github.com/efernandezpascual/alpineseeds) as a [.tree file](https://github.com/efernandezpascual/alpineseeds/blob/master/data/ALPINE.tree) that can be imported into R, or opened with software like [TreeGraph](http://treegraph.bioinfweb.info/). We have now also included a [pdf version of the tree](https://github.com/efernandezpascual/alpineseeds/blob/master/data/ALPINE.tree.pdf), so it can be visualized directly. We have indicated at the appropriate point of the text that the tree can be accessed at GitHub. We would prefer this solution to including it as a supplementary file, to avoid duplicating data sources.
